Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-12 lloveras_2020.tex
editado por Albert 12/Dic/2019 - 18:44 hs

%% Template.tex; Solar Physics
%% 
\documentclass[namedreferences]{solarphysics}
%
% spr-sola-addons available options:
%  hyperref      -- loads hyperref.sty with options (pdfborder={0 0 0 },urlcolor=blue,breaklinks)
%  nonatbib      -- do not load natbib.sty (style loads it by default)
%  solaromanenum -- makes enumerated list with roman numerals and a single right-bracket
%  linksfromyear -- puts a link on a year citation (hyperref must be loaded). Loaded by default
%  nolinksfromyear -- suppress  linksfromyear
%  optionalrh    -- for optional running title/author
%  showbiblabels -- to show bibitem label at end of bibitem (via \endbibitem command)
%
\usepackage[hyperref,optionalrh,solaromanenum]{spr-sola-addons} % For Solar Physics 
%\usepackage{epsfig}                     % For eps figures, old commands
\usepackage{graphicx}                    % For eps figures, newer & more powerfull
%\usepackage{courier}                    % Change the \texttt command to courier style
\usepackage{amssymb}                     % useful mathematical symbols
\usepackage{color}                       % For color text: \color command
\usepackage{breakurl}                    % For breaking URLs easily trough lines
\def\UrlFont{\sf}                        % define the fonts for the URLs
\usepackage{comment}
\usepackage{setspace}

\usepackage[dvipsnames]{xcolor}

%% Local definitions
%% please place your own definitions here and don't use \def but
%% \newcommand{}{} or 
%% \renewcommand{}{} if it is already defined in LaTeX
\renewcommand{\deg}{$^\circ$}
\newcommand{\mdeg}{^\circ}
\newcommand{\rsun}{R{$_\odot$}}
\renewcommand{\l}{\lambda_{\rm N}}%\lambda_
\newcommand{\mrsun}{{\rm R_\odot}}
\newcommand{\med}{{\rm Md}}
\newcommand{\avgTe}{\left<T_\textrm{m}\right>}
\newcommand{\MK}{{\rm MK}}
\newcommand{\cm}{{\rm cm}}
\newcommand{\sdev}{{\rm SD}}
\newcommand{\mean}{{\rm Mn}}
\newcommand{\deltat}{$\delta$}
\newcommand{\LDEM}{{\rm LDEM}}
\newcommand{\FBE}{{\rm FBE}}
\newcommand{\TRF}{{\rm TRF}}
\newcommand{\lN}{\lambda_N}
\newcommand{\NCB}{N_{\rm CB}}
\newcommand{\aTm}{\left< T_\textrm{m}\right>}
\newcommand{\Nqi}{N_{\rm QI}}
\newcommand{\sqravgN}{\sqrt{\langle N_{e,i}^2 \rangle}}

\newcommand{\Tefit}{T_{e,{\rm fit}}}

@@

Once the LDEM is determined at each voxel, the average squared electron density $\langle N_e^2 \rangle$ and the electron mean temperature $T_\textrm{m}$ in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,

@@

so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships \albert{were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
\temp{* Aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.} \albert{ALBERT: Yo creo que es mejor simplemente hablar de $\sqravgN$}\\
\temp{* Mejoras de la DEMT con respecto a trabajos previos}.

@@

For both rotations, the DEMT and AWSoM 3D maps of electron density $N_e$, electron mean temperature $T_\textrm{m}$ and electron temperature $T_\textrm{e}$ respectively were traced along the magnetic field lines modeled using AWSoM as described at the end of Section \ref{demt}. In the case of closed loops, results were separated into their two legs, defined as the two segments that go from the coronal base up to the apex.

For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the $N_e(r)$ data points, and a linear fit applied to the $T_m(r)$ data points, as described by

\begin{eqnarray}\label{Nfit}
N_e &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
\label{Tfit}
T_\textrm{m} &=&  \nabla_r T_m \,r\,+\,T_\textrm{0}
\end{eqnarray}

\noindent
where $h \equiv r - 1\,\mrsun$, and $a$ and $b$ are constants.

@@

%The temperature as a function of height along legs shows linear behaviors. 
In the present work we focus on lines with increasing and decreasing temperatures in linear form. In other words, we selected those legs where the pearson coefficient between temperature and height ($\rho_{T,r}$) meets $|\rho_{T,r}| > 0.5$ \temp{(with p-value less than 0.05)}. In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.

The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\nabla_r T_m\,[\MK/\mrsun]$ along each leg.
\diego{En realidad esta regresion lineal utiliza de por si los errores, pero luego tmb los uso para el test de hipotesis, quizas vale la pena ponerlo solo ahi.}

To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}). The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $T_m$ and $0.04 10^8 cm^{-3}$ for $N_e$ and legs with p-value $>0.005$ were rejected.

@@

\item 
The pearson value must comply $|\rho_{T,r}| > 0.5$.

@@

\begin{itemize}
 \item Type 0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\nabla_r T_m < 0$. %This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.

\item  Type I - Small closed field lines in all latitudes, with $\nabla_r T_m > 0$. %This class thoroughly populates the inner of the Streamer belt.

\item  Type II - Large closed field lines (meaning their apex surpasses the DEMT range of heights) in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$. %This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt.

\item Type III - Open field lines (meaning with apex out the DEMT range of heights) in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.

@@

Once the LDEM was determined for each rotation, the electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}. As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} shows the latitude-longitude maps for both tomographic results for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$. Black voxels correspond to non-reconstructed voxels (explained in Section \ref{demt}).

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively. Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

@@

 As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\nabla_r T_m$, and the height-averaged (along the loop) electron mean temperature $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $ N_e(r=1.025\,\mrsun)$ as in previous articles. In this case, for an further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,065\,\mrsun)$.

@@

Figure \ref{gradt_demt} shows histograms (normalized to the total amount of field lines) of the temperature radial gradients ($\nabla_r T_m$) for every type of line and for both rotations.
The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{Comparative statistical distributions of DEMT reults. From left to right: the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all types of legs defined in Section \ref{trace}. Results of CR2082 are shown in blue while those of CR-2208 in red. In each panel the median $m$ is indicated.}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $N_e$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$. The black curve denotes the open-close boundary.

A visual inspection of the AWSoM results shows that both reconstruction are very axysimmetric for $N_e$ and $T_e$ as well. The closed region is denser and hotter than the open region. The density and temperature gradients are maximum in the open-close boundary. The open field regions in low latitudes maintain thermodynamic values associated with open regions. CR-2208 shows a well reconstruction of the AR around latitude $+10\mdeg$ and longitude $300\mdeg$ and a slight temperature difference between the poles \temp{estoy asumiento que es una AR}. 
In both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.

@@

In the same way as in Section \ref{demt_res}, the model results were traced along the magnetic lines obtained with it. This allowed to obtain $N_e(r)$ and $T_e(r)$ along the magnetic lines and fit them to the Equations \ref{Nfit} and \ref{Tfit}.

@@

To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $N_e(r)$ and $T_e(r)$ for every type of legs.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
\caption{Average fits of $N_e(r)$ and $T_e(r)$ for legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions for CR-2082 between DEMT (blue) and AWSoM (red). From left to right: the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average $\aTm$ along the four types of legs considered in Section \ref{trace}. In each panel the median ($m$) is indicated.}
\label{histos_2082}
\end{center}
\end{figure}

@@

%For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}. For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}. As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}T_m/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv N_e(r=1.025\,\mrsun)$. Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.

@@

For each rotation, everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lat}, and the same for the northern hemisphere, showing an anti-correlation between $N_e$ at low heights and high $V_r$ at $6\,\mrsun$.

>>>>

%% Template.tex; Solar Physics
%% 
\documentclass[namedreferences]{solarphysics}
%
% spr-sola-addons available options:
%  hyperref      -- loads hyperref.sty with options (pdfborder={0 0 0 },urlcolor=blue,breaklinks)
%  nonatbib      -- do not load natbib.sty (style loads it by default)
%  solaromanenum -- makes enumerated list with roman numerals and a single right-bracket
%  linksfromyear -- puts a link on a year citation (hyperref must be loaded). Loaded by default
%  nolinksfromyear -- suppress  linksfromyear
%  optionalrh    -- for optional running title/author
%  showbiblabels -- to show bibitem label at end of bibitem (via \endbibitem command)
%
\usepackage[hyperref,optionalrh,solaromanenum]{spr-sola-addons} % For Solar Physics 
%\usepackage{epsfig}                     % For eps figures, old commands
\usepackage{graphicx}                    % For eps figures, newer & more powerfull
%\usepackage{courier}                    % Change the \texttt command to courier style
\usepackage{amssymb}                     % useful mathematical symbols
\usepackage{color}                       % For color text: \color command
\usepackage{breakurl}                    % For breaking URLs easily trough lines
\def\UrlFont{\sf}                        % define the fonts for the URLs
\usepackage{comment}
\usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[dvipsnames]{xcolor}

%% Local definitions
%% please place your own definitions here and don't use \def but
%% \newcommand{}{} or 
%% \renewcommand{}{} if it is already defined in LaTeX
\renewcommand{\deg}{$^\circ$}
\newcommand{\mdeg}{^\circ}
\newcommand{\rsun}{R{$_\odot$}}
\renewcommand{\l}{\lambda_{\rm N}}%\lambda_
\newcommand{\mrsun}{{\rm R_\odot}}
\newcommand{\med}{{\rm Md}}
\newcommand{\avgTe}{\left<\Tm\right>}
\newcommand{\MK}{{\rm MK}}
\newcommand{\cm}{{\rm cm}}
\newcommand{\sdev}{{\rm SD}}
\newcommand{\mean}{{\rm Mn}}
\newcommand{\deltat}{$\delta$}
\newcommand{\LDEM}{{\rm LDEM}}
\newcommand{\FBE}{{\rm FBE}}
\newcommand{\TRF}{{\rm TRF}}
\newcommand{\lN}{\lambda_N}
\newcommand{\NCB}{N_{\rm CB}}
\newcommand{\aTm}{\left< \Tm\right>}
\newcommand{\Nqi}{N_{\rm QI}}
\newcommand{\sqravgN}{\sqrt{\langle N_{e,i}^2 \rangle}}
\newcommand{\dr}{\triangledown_r}
\newcommand{\er}{\mathbf{e}_r}
\newcommand{\Te}{T_{\rm e}}
\newcommand{\Tm}{T_{\rm m}}
\newcommand{\Ne}{N_{\rm e}}
\newcommand{\rhoTr}{\rho(T,r)}
\newcommand{\Tefit}{T_{e,{\rm fit}}}

@@

Once the LDEM is determined at each voxel, the average squared electron density $\langle \Ne^2 \rangle$ and the electron mean temperature $\Tm$ in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,

@@

so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships \albert{were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
\temp{* Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} \albert{ALBERT: Yo creo que es mejor simplemente hablar de $\sqravgN$}\\
\temp{* Mejoras de la DEMT con respecto a trabajos previos}.

@@

For both rotations, the DEMT and AWSoM 3D maps of electron density $\Ne$, electron mean temperature $\Tm$ and electron temperature $\Te$ respectively were traced along the magnetic field lines modeled using AWSoM as described at the end of Section \ref{demt}. In the case of closed loops, results were separated into their two legs, defined as the two segments that go from the coronal base up to the apex.

For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the $\Ne(r)$ data points, and a linear fit applied to the $\Tm(r)$ data points, as described by

\begin{eqnarray}\label{Nfit}
\Ne &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
\label{Tfit}
\albert{\Tm} &=& \albert{\dr \Tm(r) \ r\,+\,T_0}
\end{eqnarray}

\noindent
\albert{where $\l$ is the electron density scale height, $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere, $\dr\equiv\er\cdot\nabla$ is the radial derivative operator (being $\er$ the heliocentric radial unit vector), and $T_0$ and $N_0$ are constants.}

@@

%The temperature as a function of height along legs shows linear behaviors. 
In the present work we focus on lines with increasing and decreasing temperatures in linear form. In other words, we selected those legs where the \albert{Pearson correlation coefficient $\rho$ between temperature $T$ and radius $r$ meets $|\rhoTr| > 0.5$}. \temp{(with p-value less than 0.05)}. In this way, those legs in which the DEMT results cannot ensure a noticeable change in temperature between the base and the apex, are discarded.

The linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg.
\diego{En realidad esta regresion lineal utiliza de por si los errores, pero luego tmb los uso para el test de hipotesis, quizas vale la pena ponerlo solo ahi.}

To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}). The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $0.04 10^8 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.

@@

\item 
The \albert{value of the Pearson correation coefficient meets $|\rhoTr| > 0.5$.}

@@

\begin{itemize}
 \item Type 0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\dr \Tm < 0$. %This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.

\item  Type I - Small closed field lines in all latitudes, with $\dr \Tm > 0$. %This class thoroughly populates the inner of the Streamer belt.

\item  Type II - Large closed field lines (meaning their apex surpasses the DEMT range of heights) in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\dr \Tm > 0$. %This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt.

\item Type III - Open field lines (meaning with apex out the DEMT range of heights) in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\dr \Tm > 0$.

@@

Once the LDEM was determined for each rotation, the electron density $\Ne$ and electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}. As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} shows the latitude-longitude maps for both tomographic results for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$. Black voxels correspond to non-reconstructed voxels (explained in Section \ref{demt}).

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT results: $\Ne$ (left panels) and $\Tm$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively. Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

@@

 As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the loop) electron mean temperature $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $ \Ne(r=1.025\,\mrsun)$ as in previous articles. In this case, for an further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,065\,\mrsun)$.

@@

Figure \ref{gradt_demt} shows histograms (normalized to the total amount of field lines) of the temperature radial gradients ($\dr \Tm$) for every type of line and for both rotations.
The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{Comparative statistical distributions of DEMT reults. From left to right: the coronal base electron density $\Ne(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all types of legs defined in Section \ref{trace}. Results of CR2082 are shown in blue while those of CR-2208 in red. In each panel the median $m$ is indicated.}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $\Ne$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$. The black curve denotes the open-close boundary.

A visual inspection of the AWSoM results shows that both reconstruction are very axysimmetric for $\Ne$ and $T_e$ as well. The closed region is denser and hotter than the open region. The density and temperature gradients are maximum in the open-close boundary. The open field regions in low latitudes maintain thermodynamic values associated with open regions. CR-2208 shows a well reconstruction of the AR around latitude $+10\mdeg$ and longitude $300\mdeg$ and a slight temperature difference between the poles \temp{estoy asumiento que es una AR}. 
In both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature.

@@

In the same way as in Section \ref{demt_res}, the model results were traced along the magnetic lines obtained with it. This allowed to obtain $\Ne(r)$ and $T_e(r)$ along the magnetic lines and fit them to the Equations \ref{Nfit} and \ref{Tfit}.

@@

To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $\Ne(r)$ and $T_e(r)$ for every type of legs.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
\caption{Average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions for CR-2082 between DEMT (blue) and AWSoM (red). From left to right: the coronal base electron density $\Ne(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average $\aTm$ along the four types of legs considered in Section \ref{trace}. In each panel the median ($m$) is indicated.}
\label{histos_2082}
\end{center}
\end{figure}

@@

%For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}. For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}. As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}\Tm/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv \Ne(r=1.025\,\mrsun)$. Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.

@@

For each rotation, everything to the south of the HCS maps down to the southern open region in the Figures \ref{perf_lat}, and the same for the northern hemisphere, showing an anti-correlation between $\Ne$ at low heights and high $V_r$ at $6\,\mrsun$.
